Perturbing SU($n$)-symmetric interactions

### 2019-10-30 collective_sun/sun_perturbation.tex
better commentary on the block-diagonal form of the two-body eigenvalue problem added simplifications of the two-body eigenvalue problem in the case of translational invariance

The two-body case requires a bit of work to re-cast as an
eigenvector/eigenvalue problem.  We begin by writing the matrix $\m v$ as a vector,
\begin{align}
  \m v = \sum_{p,q} v_{pq} \op{k}{q}
  \to \check{\m v} \equiv \sum_{p,q} v_{pq} \ket{pq},
\end{align}
and then defining the matrix
\begin{align}
  \check{\m h}
  \equiv \sum_{k,\ell} \bar h_{k\ell} \op{k\ell}
  + \sum_{k,q,\ell} h_{kq} \op{k}{q} \otimes \op{\ell},
  \label{eq:h_super_mat}
\end{align}
in terms of which the condition in \eqref{eq:v_cond_2} becomes
\begin{align}
  \check{\m h} \c \check{\m v} = \e\p{\m v} \check{\m v}.
\end{align}
Note that the matrix $\check{\m h}$ in \eqref{eq:h_super_mat} is
block-diagonal, with $N$ blocks of size $N\times N$.  The task of
constructing eigenvectors $\V_2\p{\m v}\ket\psi$ of $H_0$ and
determining their energy thus reduces to finding the eigenvectors and
eigenvalues of $N$ matrices of size $N\times N$.

>>>>

The two-body case requires a bit of work to re-cast as an
eigenvector/eigenvalue problem.  We first write the matrix $\m v$ as a
vector,
\begin{align}
  \m v = \sum_{p,q} v_{pq} \op{k}{q}
  \to \v{\m v} \equiv \sum_{p,q} v_{pq} \ket{pq},
\end{align}
and define the matrix
\begin{align}
  \check{\m h}
  \equiv \sum_{k,\ell} \bar h_{k\ell} \op{k\ell}
  + \sum_{k,q,\ell} h_{kq} \op{k\ell}{q\ell},
  \label{eq:h_super_mat}
\end{align}
in terms of which the condition in \eqref{eq:v_cond_2} becomes
\begin{align}
  \check{\m h} \c \v{\m v} = \e\p{\m v} \v{\m v}.
\end{align}
Note that the matrix $\check{\m h}$ in \eqref{eq:h_super_mat} can be
written in the block-diagonal form
\begin{align}
  \check{\m h} = \sum_\ell \m h_\ell \otimes \op{\ell},
  &&
  \m h_\ell
  \equiv \sum_{k,q}\p{\delta_{kq} \bar h_{k\ell} + h_{kq}} \op{k}{q},
\end{align}
where each block $\m h_\ell$ is an $N\times N$ matrix.  We can
diagonalize these blocks independently, and classify their
eigenvectors by corresponding eigenvalues.  ``Total'' eigenvectors
$\v{\m v}$ of $\check{\m h}$ are then essentially concatenations of
eigenvectors from within each block $\m h_\ell$ that all share the
same eigenvalue.  The task of constructing eigenvectors
$\V_2\p{\m v}\ket\psi$ of $H_0$ and determining their energy thus
reduces to finding the eigenvectors and eigenvalues of $N$ matrices
$\m h_\ell$ of size $N\times N$.  If the interaction Hamiltonian $H_0$
is translationally invariant, then
\begin{align}
  \m h_{\ell} = \m\omega_\ell \c \m h_0 \c \m\omega_\ell^\dag,
  &&
  \m\omega_\ell \equiv \sum_k \op{k+\ell}{k},
\end{align}
which implies that we need only find the eigenvectors and eigenvalues
of a single block $\m h_0$, after which we can determine the
eigenvectors of any block simply by appropriate applications of the
shift matrix $\m\omega_\ell$.
